Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-09-29 Manuscript/manuscript.tex
One more comment

It was found in the original work~\cite{altenbach84} that 
a ternary complex binding model (i.e.~2~POPC:1~\ce{Ca^{2+}})
provides the best fit to experimental measurements of all considered models in that study. 
In such a model, there is a linear relationship between quantities 
$C_b$, mole fraction of bound \ce{Ca^{2+}} per POPC, and $\sqrt{C_b/C_I}$, 
where $C_I$ is the concentration of free cations at the plane of ion binding~\cite{altenbach84}.
The concentration $C_b$ was obtained from an extrapolation of linear relation 
between deuterium NMR measurements and atomic absorption spectroscopy for low concetrations of \ce{CaCl2}.
Such an extrapolation is valid as long as the mode of \ce{Ca^{2+}} binding 
remains constant throughout the extrapolation range. 
The concentration $C_I$ is determined by using the surface potential by using the Boltzmann equation.
However, Boltzmann theory yields inaccurate results
for divalent cations like \ce{Ca^{2+}}~\cite{Andelman1995}. 
An atomistic simulation, on the other hand, provides these quantities directly without severe assumptions. 
Hence we hypothesise that the discrepancy between the results in the experiment~\cite{altenbach84} and 
our simulations likely lays in the fact that 
the assumptions and relations used for determinig concentrations $C_b$ and $C_I$ in the experiment~\cite{altenbach84}
gradually do not hold for higher concentrations of \ce{Ca^{2+}}.

>>>>

It was found in the original work~\cite{altenbach84} that 
a ternary complex binding model (i.e.~2~POPC:1~\ce{Ca^{2+}})
provides the best fit to experimental measurements of all considered models in that study. 
In such a model, there is a linear relationship between quantities 
$C_b$, mole fraction of bound \ce{Ca^{2+}} per POPC, and $\sqrt{C_b/C_I}$, 
where $C_I$ is the concentration of free cations at the plane of ion binding~\cite{altenbach84}.
The concentration $C_b$ was obtained from an extrapolation of linear relation 
between deuterium NMR measurements and atomic absorption spectroscopy for low concetrations of \ce{CaCl2}.
Such an extrapolation is valid as long as the mode of \ce{Ca^{2+}} binding 
remains constant throughout the extrapolation range. 
The concentration $C_I$ is determined by using the surface potential by using the Boltzmann equation.
However, Boltzmann theory yields inaccurate results
for divalent cations like \ce{Ca^{2+}}~\cite{Andelman1995}. 
An atomistic simulation, on the other hand, provides these quantities directly without severe assumptions.
\todo{Did you really calculate the $C_I$ from simulations without severe assumptions?
Note that this conctration at the plane of biding, which do not equal the concentration of free cations.}
Hence we hypothesise that the discrepancy between the results in the experiment~\cite{altenbach84} and 
our simulations likely lays in the fact that 
the assumptions and relations used for determinig concentrations $C_b$ and $C_I$ in the experiment~\cite{altenbach84}
gradually do not hold for higher concentrations of \ce{Ca^{2+}}.
